Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-25 article/draft.tex
cosmetic changes in the discussion + figure size

\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.4]{../figure/facebook_crowdtangle_trump.png}
		%\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/lifesite_domain.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}[h]
\hspace{-2em}
	%\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/OANN_videos_yt.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/OANN_views_yt.png} 
	%\end{multicols}
	\caption{Left Panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Right Panel: accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

	%\begin{multicols}{1}
		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_1.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.25]{../figure/facebook_crowdtangle_infowars_2.png} 
	%\end{multicols}

	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API. The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars. (Top panel) Number of daily posts. (Bottom panel) Engagement metrics: average number of reactions, shares and comments per post. }
	\label{infowars1}
\end{figure}

@@

	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{../figure/facebook_buzzsumo_thebl_1.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{../figure/facebook_buzzsumo_thebl_2.png} 
	%\end{multicols}

	\caption{Articles from The Beauty of Life website (thebl.com) published between January 1, 2019 and June 15, 2021 and gathered from the Buzzsumo API. Left panel: Facebook engagement metrics (average number of reactions, shares and comments per article). Right panel: Number of articles published per day. The red line marks the date of December 1, 2019. }
	\label{fb_bl}
\end{figure}
%BuzzSumo is a commercial content database that tracks the volume of user interactions with internet content on Facebook, Twitter, and other social media platforms.

@@

%To illustrate we provide two examples linked to the Twitter accounts of the websites $globalresearch.ca$ and $off$-$guardian.org$. Both websites have several failed fact-checks according to \href{https://iffy.news}{iffy.news} - a website which provides a database of websites with low factual reporting levels.\footnote{For $globalresearch.ca$ see \href{https://mediabiasfactcheck.com/global-research/}{https://mediabiasfactcheck.com/global-research/} and for $off-guardian.org$ see \href{https://mediabiasfactcheck.com/offguardian/}{https://mediabiasfactcheck.com/offguardian/}.  }
\begin{figure}[h]
	\centering
		%\begin{multicols}{1}	
					\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
		%\end{multicols}
		%\begin{multicols}{1}
					\includegraphics[scale=0.32]{./img/globalresearch/tweet.png} 
		%\end{multicols}
		\caption{Screenshots taken on June 14, 2021. Left Panel: screenshot that shows that no results can be found when searching for articles linked to the domain name $globalresearch.ca$ via the Twitter search box. Right Panel: example of a tweet posted on June $14$ containing the domain name {\it globalresearch.ca}. }
		\label{fig3}
\end{figure}

@@

\begin{figure}[h]
\centering
		\includegraphics[scale=0.27]{../figure/globalresearch_domain_2021-08-17.jpg} 
		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Data collected via the Twitter API v2 on August $17$, 2021.   }
\label{fig4}
\end{figure}

@@

%what about with search terms: most recommended channels?

@@

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.6]{./img/channel_youtube.png} 
	\end{center}
	\caption{Top ten recommended channels among the $1$ $562$ different channels, that have posted the recommended videos in our dataset.}
	\label{channels_yt}
\end{figure}

@@

Furthermore, it is likely that most interventions used to tackle online misinformation correspond to interventions that were designed for earlier policy areas.
To illustrate, YouTube explicitly states
\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.}
that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
Hence interventions such as content deletion or account suspension, might be efficient for policy areas for which they were designed, such as Adult Nudity \& Sexual Activity or Hate Speech. Nevertheless, tackling online misinformation might need adapted interventions.
Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation (Rogers (2020)~\cite{rogers2020}, Robins-Early (2019)~\cite{huffpost}).

@@

How to best tackle online misinformation is an active area of research, and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook and Rand (2021)~\cite{pennycook2021psychology}). 
Adding fact-checking labels to controversial content is certainly the intervention whose effectiveness was the most studied so far. 
It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings (Yaqub (2020)~\cite{yaqub2020effects}, Sharevski (2021)~\cite{sharevski2021misinformation}).
Moreover, a fact-checking label can lead to unpredicted consequences depending on the perception of the person reading it.
On Facebook, Twitter and YouTube, fact-checking messages are currently applied only to some content, while the rest of the platform remains unlabelled. 
Such sparce application of warnings can lead to an `implied truth' effect where users may assume that content without warnings have actually been verified and shown to be true (Pennycook et al. (2020)~\cite{pennycook2020implied}).
Using another approach, Mosleh et al. (2021)~\cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false tweets with links to fact-checking websites.
They observed a decrease in quality and accuracy of the content subsequently shared by the corrected user. 
These works highlight the necessity to investigate potential unintended effects of well-meaning interventions.
The methods presented in this paper can help to monitor not only the platforms' actions against misinformations, but also their subsequent consequences in real-life settings.

@@

\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Flags, Notice \\ and Information Panels \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}    \end{tabular}                            \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}} \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}    \end{tabular}    \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}   \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}  \end{tabular}                            \\ \hline

>>>>

\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_trump.png}
		%\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

\begin{figure}[h]
\hspace{-2em}
%\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/lifesite_domain.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}[h]
\hspace{-2em}
	%\centering
		\includegraphics[scale=0.32]{../figure/OANN_videos_yt.png}
		\includegraphics[scale=0.32]{../figure/OANN_views_yt.png} 
	\caption{Left Panel: Number of YouTube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Right Panel: accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

\begin{figure}[h]
\hspace{-2em}
	%\centering
		\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_infowars_1.png}
		\includegraphics[scale=0.32]{../figure/facebook_crowdtangle_infowars_2.png} 
	\caption{Public Facebook posts sharing an Infowars link in $2019$ and $2020$ collected from the CrowdTangle API. The red line marks the date of May $2$, 2019, when Facebook has announced the ban regarding Infowars. (Top panel) Number of daily posts. (Bottom panel) Engagement metrics: average number of reactions, shares and comments per post. }
	\label{infowars1}
\end{figure}

@@

\begin{figure}[h]
\hspace{-2em}
	%\centering
		\includegraphics[scale=0.32]{../figure/facebook_buzzsumo_thebl_1.png}
		\includegraphics[scale=0.32]{../figure/facebook_buzzsumo_thebl_2.png} 
	\caption{Articles from The Beauty of Life website (thebl.com) published between January 1, 2019 and June 15, 2021 and gathered from the Buzzsumo API. Left panel: Facebook engagement metrics (average number of reactions, shares and comments per article). Right panel: Number of articles published per day. The red line marks the date of December 1, 2019. }
	\label{fb_bl}
\end{figure}

@@

\begin{figure}[h]
	\centering
%\hspace{-2em}
	\includegraphics[scale=0.32]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
	\includegraphics[scale=0.32]{./img/globalresearch/tweet.png}

	\caption{Screenshots taken on June 14, 2021. Left Panel: screenshot that shows that no results can be found when searching for articles linked to the domain name $globalresearch.ca$ via the Twitter search box. Right Panel: example of a tweet posted on June $14$ containing the domain name {\it globalresearch.ca}. }
		\label{fig3}
\end{figure}

@@

\begin{figure}[h]
%\centering
\hspace{-2em}
		\includegraphics[scale=0.32]{../figure/globalresearch_domain_2021-08-17.jpg} 
		\includegraphics[scale=0.32]{../figure/globalresearch_domain_engagement_2021-08-17.jpg}
\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Data collected via the Twitter API v2 on August $17$, 2021.   }
\label{fig4}
\end{figure}

@@

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.45]{./img/channel_youtube.png} 
	\end{center}
	\caption{Top ten recommended channels among the $1$ $562$ different channels, that have posted the recommended videos in our dataset.}
	\label{channels_yt}
\end{figure}

@@

@@

Furthermore, it is likely that most interventions used to tackle online misinformation correspond to interventions that were designed for earlier policy areas.
To illustrate, YouTube explicitly states
\footnote{See {\it What policies exist to fight misinformation on Youtube?} \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}.}
that: ``Several policies in our Community Guidelines are directly applicable to misinformation'', such as the deceptive practices, impersonation and hate speech policies.
Hence interventions such as content deletion or account suspension, might be efficient for policy areas for which they were specifically designed, such as the policy area {\it Adult Nudity \& Sexual Activity}. Nevertheless, tackling online misinformation might need adapted interventions.
Namely, account suspensions or content deletion motivated by the spread of inaccurate information can be perceived as censorship by the targeted users. In particular, such interventions can generate platform migrations towards new alternative social media platforms (e.g. Telegram, Gab, Minds) with little or no content moderation (see Rogers (2020)~\cite{rogers2020}).

@@

Finally, the means to tackle online misinformation is an active area of research and developing effective interventions against misinformation depends on understanding the psychology of interacting with social media (Pennycook and Rand (2021)~\cite{pennycook2021psychology}). 
Adding fact-checking labels to controversial content is certainly the intervention whose effectiveness was the most studied so far. 
It was shown that credibility indicators do reduce misperceptions and sharing, although their impact varied vastly depending on the presentation of the warnings (see Yaqub (2020)~\cite{yaqub2020effects} and Sharevski (2021)~\cite{sharevski2021misinformation}).
Moreover, a fact-checking label can lead to unpredicted consequences depending on the perception of the person reading it.
On Facebook, Twitter and YouTube, fact-checking messages are currently applied only to some content, while the rest of the content on a given platform remains naturally unlabelled. 
Such sparse application of warnings can lead to an ``implied truth'' effect, where users may assume that content without warnings have actually been verified and shown to be true (Pennycook et al. (2020)~\cite{pennycook2020implied}).
Using a different approach, Mosleh et al. (2021)~\cite{mosleh2021perverse} identified Twitter users sharing false news and replied to their false tweets with links redirecting to fact-checking websites.
They observed a decrease in the quality and accuracy of the content subsequently shared by the corrected user. 
These research papers highlight the necessity to investigate potential unintended effects of well-meaning interventions.
The methods presented in this paper can help to monitor not only the platforms' actions against misinformation, but also their subsequent consequences in real-life settings.

@@

\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}} Flags, Notice \\ and Information Panels \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}}  \href{https://www.facebook.com/business/help/341102040382165}{https://www.facebook.com/business/help/341102040382165}   \end{tabular}                            \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   &  \begin{tabular}[c]{@{}cl@{}} \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}    \end{tabular}    \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \begin{tabular}[c]{@{}cl@{}}   \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}  \end{tabular}                            \\ \hline
